A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2022-11-07 pilot-publication/manuscript.Rmd
Update manuscript

## Resident Participant Outcomes
A total of X residents were trained during this pilot. Overall their
confidence in managing trauma patients was X (IQR X - X) on

## Feasibility Outcomes

@@

# Competing Interests
Several authors are Advanced Trauma Life Support or Primary Trauma Care instructors

>>>>

## Resident Participant Outcomes
A total of X residents were trained during this pilot. Overall their
confidence in managing trauma patients was X (IQR X - X) on a 10 point
Likert scale with 10 being most confident. In the post training
period, the confidence in the ATLS arm was X (IQR X - X), compared to
X (IQR X - X) in the PTC arm, and X (IQR X - X) in the standard care
arm.

## Feasibility Outcomes
Out of X potentially eligible patients, X (X%) patients were enrolled
in the study. Out of X potentially eligible residents, X (X%) were
enrolled in the study. The loss to follow up rate was X, with X out of
X patients not completing 30 day follow up. Among residents the pass
rate, after two attempts, was X (X%). The missing data rate ranged
from X to X, with details per variable and outcome in Table X. The
differences in distributions between observed and extracted data, for
variables that were collected through observation or interview, are
shown in Table X.

## Community Consultations
The results of interviews with patients, caregivers and social workers
will be published separately. Residents felt that...

@@

# Competing Interests
Several authors are Advanced Trauma Life Support or Primary Trauma
Care instructors.
